### 2017-07-19 profiles_examples.Rmd
Diff in props is working (All examples in README working)

Infer: a grammar for statistical inference

Using a sample of profiles from the `okcupiddata` package

---

The objective of this package is to perform statistical inference using a grammar that illustrates the underlying concepts and a format that coheres with the `tidyverse`.

@@

Two categorical variables (diff in proportions) (not yet implemented)

```
prof_small %>%
  specify(sex ~ frisco) %>%
  generate(reps = 1000, type = "bootstrap") %>%
  calculate(stat = "diff in prop")
```

>>>>

@@

Two categorical variables (diff in proportions)

```{r}
prof_small %>%
  specify(sex ~ frisco) %>%
  generate(reps = 1000, type = "bootstrap") %>%
  calculate(stat = "diff in props") %>% 
  visualize()
```
